Read quality check

### 2019-02-23 writing/qual-check.Rmd
switch back to using UPPMAX module system for texlive because the conda version doesn't seem to work.
Use global theming

```{r setup, include = FALSE}
library(magrittr)
library(tidyverse)
library(glue)
library(Biostrings)
library(ShortRead)
library(ggplot2)
library("scales")
library(drake)
knitr::opts_chunk$set(echo = FALSE, device = "tikz")
```

@@

## Minimum quality score
```{r}
ggplot(reads_subset, aes(x = minq,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Minimum quality score",
                     # trans = reverselog_trans(10),
                     # limits = c(NA, 1e-5),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete() +
  theme_bw()
```

@@

ggplot(reads_subset, aes(x = erate,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors per base",
                     trans = reverselog_trans(10),
                     limits = c(NA, 1e-5),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete() +
  theme_bw()
```

## Expected number of errors
```{r}
ggplot(reads_subset, aes(x = eexp,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors",
                     trans = reverselog_trans(10),
                     limits = c(NA, 0.1),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete() +
  theme_bw()
```

@@

```{r}
ggplot(reads_subset, aes(x = p.noerr,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expectation of being error-free",
                     # trans = log_trans(10),
                     limits = c(0, 1),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete() +
  theme_bw()
```

@@

```{r}
ggplot(reads_subset, aes(x = length,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_log10(name = "Length (bp)",
                limits = c(50, NA),
                oob = squish) +
  scale_y_continuous(name = "Fraction Greater than length") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete() +
  theme_bw()
```

## Read length density
```{r}
ggplot(reads_subset, aes(x = length,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(stat = "density") +
  scale_x_log10(name = "Length (bp)",
                limits = c(50, NA),
                oob = squish) +
  scale_y_continuous(name = "count") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete() +
  theme_bw()
```

>>>>

```{r setup, include = FALSE}
library(magrittr)
library(tidyverse)
library(glue)
library(Biostrings)
library(ShortRead)
library(ggplot2)
library("scales")
library(drake)
knitr::opts_chunk$set(echo = FALSE, device = "tikz")
theme_set(theme_bw(base_size = 24) + theme(legend.direction = "vertical"))
```

@@

## Minimum quality score
```{r}
ggplot(reads_subset, aes(x = minq,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Minimum quality score",
                     # trans = reverselog_trans(10),
                     # limits = c(NA, 1e-5),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
```

@@

ggplot(reads_subset, aes(x = erate,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors per base",
                     trans = reverselog_trans(10),
                     limits = c(NA, 1e-5),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
```

## Expected number of errors
```{r}
ggplot(reads_subset, aes(x = eexp,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expected number of errors",
                     trans = reverselog_trans(10),
                     limits = c(NA, 0.1),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
```

@@

```{r}
ggplot(reads_subset, aes(x = p.noerr,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_continuous(name = "Expectation of being error-free",
                     # trans = log_trans(10),
                     limits = c(0, 1),
                     oob = squish) +
  scale_y_continuous(name = "Fraction passing") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
```

@@

```{r}
ggplot(reads_subset, aes(x = length,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(aes(y = 1 - ..y..), stat = "ecdf") +
  scale_x_log10(name = "Length (bp)",
                limits = c(50, NA),
                oob = squish) +
  scale_y_continuous(name = "Fraction Greater than length") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
```

## Read length density
```{r}
ggplot(reads_subset, aes(x = length,
                  linetype = Dataset,
                  group = paste(Dataset, Region),
                  color = Region)) +
  geom_line(stat = "density") +
  scale_x_log10(name = "Length (bp)",
                limits = c(50, NA),
                oob = squish) +
  scale_y_continuous(name = "count") +
  scale_color_viridis_d(option = "C") +
  scale_linetype_discrete()
```
